Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-14 paper/paper.tex
Abstract

\documentclass{llncs}
\usepackage[pass]{geometry}

\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{tikz}

@@

\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}[1]{\cite{#1}}

@@

\title{Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms}

\author{
    Ruth Hoffmann \inst{1}
    \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1, EP/M508056/1, and EP/M508056/1]} \inst{2}
    \and Samba Ndojh Ndiaye\thanks{This work was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)} \inst{3}
    \and Patrick Prosser \inst{2}
    \and Craig Reilly \samethanks[1] \inst{2}
    \and Christine Solnon\samethanks[2]\inst{4} \and James Trimble\samethanks[1] \inst{2}}

\institute{
    University of St Andrews, St Andrews, Scotland
    \and University of Glasgow, Glasgow, Scotland
    \and Universit\'e Lyon 1, LIRIS, UMR5205, F-69621, France
    \and INSA-Lyon, LIRIS, UMR5205, F-69621, France \\
    \email{c.mccreesh.1@research.gla.ac.uk}}

\begin{document}

@@

\begin{abstract}

\end{abstract}

@@

\begin{figure}[p]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}

@@

\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for unlabelled, undirected graphs. The histograms show the
    distribution of speedups for instances whose sequential runtime is at least $50$ milliseconds
    and no more than $100$ seconds (and so they under-represent superlinear speedups slightly).}
\end{figure}

\begin{figure}[t]
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-labelled graphs.}
\end{figure}

\begin{figure}[t]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure}

\begin{figure}[t]
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure}

\begin{figure}[p]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure}

@@

\bibliographystyle{splncs03}
\bibliography{dblp}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{showframe}

\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{tikz}

@@

@@

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[$\textnormal{IA}^3$ 2017]{Seventh Workshop on Irregular Applications: Architectures and Algorithms}{November 2017}{Denver, Colorado USA}
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{666.00}

\begin{document}
\title[Observations from Parallelising Three Subgraph Algorithms]{Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms}
\titlenote{This work was supported by the Engineering and Physical Sciences
    Research Council [grant numbers EP/K503058/1, EP/M508056, and EP/P026842/1] and the ANR project
SoLStiCe (ANR-13-BS02-0002-01)}

\author{Ruth Hoffmann}
\affiliation{%
    \institution{University of St Andrews}
    \city{St Andrews, Scotland}
}

\author{Ciaran McCreesh}
\affiliation{%
    \institution{University of Glasgow}
    \city{Glasgow, Scotland}
}
\email{ciaran.mccreesh@glasgow.ac.uk}

\author{Samba Ndojh Ndiaye}
\affiliation{
    \institution{Universit\'e Lyon 1, LIRIS, UMR5205}
    \postcode{F-69621, France}
}

\author{Patrick Prosser}
\affiliation{%
    \institution{University of Glasgow}
    \city{Glasgow, Scotland}
}

\author{Craig Reilly}
\affiliation{%
    \institution{University of Glasgow}
    \city{Glasgow, Scotland}
}

\author{Christine Solnon}
\affiliation{
    \institution{INSA-Lyon, LIRIS, UMR5205}
    \city{F-69621, France}
}

\author{James Trimble}
\affiliation{%
    \institution{University of Glasgow}
    \city{Glasgow, Scotland}
}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{R. Hoffmann et al.}

\begin{abstract}
    We discuss our experiences adapting three recent algorithms for maximum common (connected) subgraph
    problems to exploit multi-core parallelism. We consider the effects of different work
    distribution strategies and their interaction with value-ordering heuristics, and propose a
    search method which is risk-free, reproducible, and scalable, as well as beneficial. Our results
    show that each algorithm can be parallelised successfully using this strategy, with the
    multi-core algorithms we create being clearly better than the sequential ones. We then look in
    more detail at the results, on an instance by instance basis, and discuss how we should be
    measuring speedups for these kinds of algorithm.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
\end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

% \keywords{ACM proceedings, \LaTeX, text tagging}

@@

@@

\begin{figure*}[p]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}

@@

\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for unlabelled, undirected graphs. The histograms show the
    distribution of speedups for instances whose sequential runtime is at least $50$ milliseconds
    and no more than $100$ seconds (and so they under-represent superlinear speedups slightly).}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-labelled graphs.}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure*}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{dblp}
